Integration of national demographic-disturbance relationships into local caribou population viability projections can reduce uncertainty and inform monitoring decisions

### 2024-10-16 analysis/paper/paper.Rmd

Figure 6: The expected value of sample information (EVSI) varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), the amount of interannual variation (high: $v_R=0.46,v_S=0.087$, low: $v_R=0.23,v_S=0.0435$), and monitoring effort. When disturbance is high EVSI is low, indicating that local sampling does not change predicted status.Where disturbance is lower, EVSI increases with the number of years of monitoring and the number of collars, but there are diminishing returns on additional monitoring as the number of years increases. Negative EVSI values indicate that the posterior population viability prediction is less certain than the prior prediction. See Figure \@ref(fig:figStatusErrors) for additional scenario details.

>>>>

Figure 6: The expected value of sample information (EVSI) varies with the amount of anthropogenic disturbance (columns), the number of years projected (rows), the amount of interannual variation (high: $v_R=0.46,v_S=0.087$, low: $v_R=0.23,v_S=0.0435$), and monitoring effort. When disturbance is high EVSI is low, indicating that local sampling does not change predicted status. Where disturbance is lower, EVSI increases with the number of years of monitoring and the number of collars, but there are diminishing returns on additional monitoring as the number of years increases. Negative EVSI values indicate that the posterior population viability prediction is less certain than the prior prediction. See Figure \@ref(fig:figStatusErrors) for additional scenario details.
